Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-08 draft.tex

Although \cite{Knudsen} develops an adjunction between Lie and $\EE_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
in any presentable symmetric monoidal stable $\infty$-category $\cC$,
we only work in the infinity category of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero.
We summarize Knudsen's result in this setting as follows.

@@

When $k$ is $\RR$ or $\CC$, 
the enveloping $\EE_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
\[
\bU_n \fg(V) = \cliels(\Omega^*_c(V) \otimes \fg)
\]
to each open set $V \subset \RR^n$.
\end{thm}

>>>>

Although \cite{Knudsen} develops an adjunction between Lie and $\EE_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
in any presentable symmetric monoidal stable $\infty$-category $\cC$,
we only work in the $\infty$-category of chain complexes $(\Mod_k, \otimes_k)$, 
where $k$ is a field of characteristic zero.
We summarize Knudsen's result in this setting as follows.

@@

When $k$ is $\RR$ or $\CC$, 
the enveloping $\EE_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
\[
\bU_n \fg(V) = \cliels(\Omega^\bu_c(V) \otimes \fg)
\]
to each open set $V \subset \RR^n$.
\end{thm}
